\documentclass[12pt]{article}
\usepackage[a4paper, margin=0.5in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{ebgaramond}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{bbm}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{tikz-cd}
\usepackage{yfonts}
\usepackage{mathrsfs}
\newcommand{\prob}[1]{\noindent {\bf #1}.}
\newcommand{\abs}[1]{\left| #1  \right|}
\newcommand{\goth}[1]{\textfrak{#1}}
\newcommand{\spec}[1]{\text{Spec}~#1}
\newcommand{\pic}[1]{\text{Pic}~#1}
\newcommand{\proj}[1]{\text{Proj}~#1}
\newcommand{\im}[1]{\text{im}\hspace{1pt}#1}
\newcommand{\coker}[1]{\text{coker}\hspace{1pt}#1}
\newcommand{\Supp}[1]{\text{Supp}(#1)}
\newcommand{\height}[1]{\text{height}~#1}
\newcommand{\fF}{\mathscr{F}}
\newcommand{\gF}{\goth{F}}
\newcommand{\fG}{\mathscr{G}}
\newcommand{\A}{\mathbb{A}}
\newcommand{\OO}{\mathscr{O}}
\newcommand{\fE}{\mathscr{E}}
\newcommand{\PP}{\mathbf{P}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\C}{\mathbf{C}}
\newcommand{\Q}{\mathbf{Q}}
\newcommand{\N}{\mathbf{N}}
\newcommand{\Z}{\mathbf{Z}}
\newcommand\restr[2]{{% we make the whole thing an ordinary symbol
  \left.\kern-\nulldelimiterspace % automatically resize the bar with \right
  #1 % the function
  \vphantom{\big|} % pretend it's a little taller at normal size
  \right|_{#2} % this is the delimiter
  }}
\DeclareMathOperator{\Hom}{Hom}
\newcommand\isomto{\stackrel{\sim}{\smash{\longrightarrow}\rule{0pt}{0.4ex}}}

\begin{document}
\begin{enumerate} [label=\textbf{\arabic*.}, leftmargin=0em]

% * 8.1, 8.2, 8.6

\item Let $X$ be a noetherian scheme, $Y$ a closed subscheme, and $\hat{X}$ the completion of $X$ along $Y$. We call the ring $\Gamma(\hat{X}, \OO_{\hat{X}})$ the ring of \textit{formal-regular functions} on $X$ along $Y$. In this exercise we show that if $Y$ is a connected, nonsingular, positive dimensional subvariety of $X = \PP_k^n$ over an algebraically closed field $k$, then $\Gamma(\hat{X}, \OO_{\hat{X}}) = k$.
\begin{itemize}
    \item[(a)] Let $\mathscr{J}$ be the ideal sheaf of $Y$. Use (8.13) and (8.17) to show that here is an inclusion of sheaves on $Y, \mathscr{J} / \mathscr{J}^2 \hookrightarrow \OO_Y(-1)^{n + 1}$.
    \item[(b)] Show that for any $r \geq 1$, $\Gamma(Y, \mathscr{J}^r / \mathscr{J}^{r + 1}) = 0$.
    \item[(c)] Use the exact sequences
    \begin{equation*}
        0 \to \mathscr{J}^r / \mathscr{J}^{r + 1} \to \OO_X / \mathscr{J}^{r + 1} \to \OO_X / \mathscr{J}^r \to 0
    \end{equation*}
    and induction on $r$ to show that $\Gamma(Y, \OO_X/\mathscr{J}^r) = k$ for all $r \geq 1$.
    \item[(d)] Conclude that $\Gamma(\hat{X}, \OO_{\hat{X}}) = k$.
\end{itemize}

\item Use the result of (Ex. 9.1) to prove the following geometric result. Let $Y \subseteq X = \PP_k^n$ be as above, and let $f : X \to Z$ be a morphism of $k$-varieties. Suppose that $f(Y)$ is a single closed point $P \in Z$. Then $f(X) = P$ also.

\item Prove the analogue of (5.6) for formal schemes, which says, if $\mathfrak{X}$ is an affine formal scheme, and if
\begin{equation*}
    0 \to \mathfrak{F}' \to \mathfrak{F} \to \mathfrak{F}'' \to 0
\end{equation*}
is an exact seuqnece of $\OO_\mathfrak{X}$-modules, and if $\mathfrak{F}'$ is coherent, then the sequence of global sections
\begin{equation*}
    0 \to \Gamma(\mathfrak{X}, \mathfrak{F}') \to \Gamma(\mathfrak{X}, \mathfrak{F}) \to \Gamma(\mathfrak{X}, \mathfrak{F}'') \to 0
\end{equation*}
is exact. For the proof, proceed in the following steps.
\begin{itemize}
    \item[(a)] Let $\mathfrak{J}$ be an ideal of definition for $\mathfrak{X}$, and for each $n > 0$ consider the exact sequence
    \begin{equation*}
        0 \to \mathfrak{F}'/\mathfrak{J}^n \mathfrak{F}' \to \mathfrak{F} / \mathfrak{J}^n \mathfrak{F} \to \mathfrak{F}'' \to 0.
    \end{equation*}
    Use (5.6), slightly modified, to show that for every open affine subset $\mathfrak{U} \subseteq \mathfrak{X}$, the sequence
    \begin{equation*}
        0 \to \Gamma(\mathfrak{U}, \mathfrak{F}'/\mathfrak{J}^n \mathfrak{F}') \to \Gamma(\mathfrak{U}, \mathfrak{F}/\mathfrak{J}^n \mathfrak{J}) \to \Gamma(\mathfrak{U}, \mathfrak{F}'') \to 0
    \end{equation*}
    is exact.
    \item[(b)] Now pass to the limit, using (9.1), (9.2), and (9.6). Conclude that $\gF \cong \varprojlim \gF / \mathfrak{J} \fF$ and that the sequence of global sections above is exact.
\end{itemize}

\item Use (Ex. 9.3) to prove that if
\begin{equation*}
    0 \to \gF' \to \gF \to \gF'' \to 0
\end{equation*}
is an exact sequence of $\OO_\mathfrak{X}$-modules on a noetherian formal scheme $\mathscr{X}$, and if $\gF', \gF''$ are coherent, then $\fF$ is coherent.

\item If $\fF$ is a coherent sheaf on a noetherian formal scheme $\mathscr{X}$, which can be generated by global sections, show in fact that it can generated by a finite number of its global sections.

\item Let $\goth{X}$ be a noetherian formal scheme, let $\goth{J}$ be an ideal of definition, and for each $n$, let $Y_n$ be the scheme $(\goth{X}, \OO_\goth{X} / \goth{J}^n)$. Assume that the inverse system of groups $(\Gamma(Y_n, \OO_{Y_n}))$ satisfies the Mittag-Leffler condition. Then prove that $\pic{\goth{X}} = \varprojlim \pic{Y_n}$. As in the case of a scheme, we define $\pic{\goth{X}}$ to be the group of locally free $\OO_\goth{X}$-modules of rank $1$ under the operation $\otimes$. Proceed in the following steps.
\begin{itemize}
    \item[(a)] Use the fact that $\text{ker}(\Gamma(Y_{n + 1}, \OO_{Y_{n + 1}})) \to \Gamma(Y_n, \OO_{Y_n})$ is a nilpotent ideal to show that the inverse system $(\Gamma(Y_n, \OO_{Y_n}^*))$ of units in the respective rings also satisfies (ML).
    \item[(b)] Let $\gF$ be a coherent sheaf of $\OO_\goth{X}$-modules, and assume that for each $n$, there is some isomorphism $\varphi_n : \gF / \goth{J}^n \gF \cong \OO_{Y_n}$. Be careful, because the $\varphi_n$ may not be compatible with the maps in the two inverse systems $(\gF / \goth{J}^n \gF)$ and $(\OO_{Y_n})$! Then show that there is an isomorphism $\gF \cong \OO_\goth{X}$. Conclude that the natural map $\pic{\goth{X}} \to \varprojlim{\pic{Y_n}}$ is injective.
    \item[(c)] Given an invertible sheaf $\mathscr{L}_n$ on $Y_n$ for each $n$, and given isomorphism $\mathscr{L}_{n + 1} \otimes \OO_{Y_n} \cong \mathscr{L}_n$, construct maps $\mathscr{L}_{n'} \to \mathscr{L}_n$ for each $n' \geq n$ so as to make an inverse system, and show that $\goth{L} = \varprojlim \mathscr{L}_n$ is a coherent sheaf on $\goth{X}$. Then show that $\goth{L}$ is locally free of rank $1$, and thus conclude that the map $\pic{\goth{X}} \to \varprojlim \pic{Y_n}$ is surjective. Again be careful, because even though each $\mathscr{L}_n$ is locally free of rank $1$, the open sets needed to make them free might get smaller and smaller with $n$.
    \item[(d)] Show that the hypothesis ``$(\Gamma(Y_n, \OO_{Y_n}))$ satisfies (ML)" is satisfied if either $\goth{X}$ is affine, or each $Y_n$ is projective over a field $k$.
\end{itemize}

\end{enumerate}
\end{document}